---
title: "Course Project: Shiny Application and Reproducible Pitch"
author: "Jones"
date: "2017-05-07"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Instructions

This peer assessed assignment has two parts. First, you will create a Shiny application and deploy it on Rstudio's servers. Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

## Data Use in Project: Air Quality

Daily air quality measurements in New York, May to September 1973.

- Ozone: Mean ozone in parts per billion from 1300 to 1500 hours at Roosevelt Island

- Solar.R: Solar radiation in Langleys in the frequency band 4000–7700 Angstroms from 0800 to 1200 hours at Central Park

- Wind: Average wind speed in miles per hour at 0700 and 1000 hours at LaGuardia Airport

- Temp: Maximum daily temperature in degrees Fahrenheit at La Guardia Airport.

## Data Sample

```{r cars, echo = TRUE}
summary(airquality)
```

## Final output

Below Shiny Application show the trend that how Ozone affect Temperature per month

<https://jonci.shinyapps.io/firstApp/>

Below github link show the original code for Shiny Application

<>



